Differential Expression - testing CQN

### 2020-08-26 testing/test_CQN_HBCC.Rmd
initial commit
fix plot labels

```{r coef}
# Specify which variable to test
coef = "DxSCZ"
# coef = "Reported_GenderMale"

@@

plot_grid(fig2, fig2a, fig2, ncol=3)
```

@@

fig2a = ggplot(df, aes(percentage_gene_gc_content, pmin(1, pmax(-1,logFC)))) + geom_point() + theme_bw() + geom_smooth(method="loess", se=FALSE) + ggtitle("NEW.COUNTS + CQN (offset)") + ylab("logFC")  + theme(aspect.ratio=1)

fig2b = ggplot(df, aes(log10(Length), pmin(1, pmax(-1,logFC)))) + geom_point() + theme_bw() + geom_smooth(method="loess", se=FALSE) + ggtitle("NEW.COUNTS + CQN (offset)") + ylab("logFC") + theme(aspect.ratio=1)

>>>>

```{r coef}
# Specify which variable to test
# coef = "DxSCZ"
coef = "Reported_GenderMale"

@@

@@

fig3a = ggplot(df, aes(percentage_gene_gc_content, pmin(1, pmax(-1,logFC)))) + geom_point() + theme_bw() + geom_smooth(method="loess", se=FALSE) + ggtitle("NEW.COUNTS + CQN (offset)") + ylab("logFC")  + theme(aspect.ratio=1)

fig3b = ggplot(df, aes(log10(Length), pmin(1, pmax(-1,logFC)))) + geom_point() + theme_bw() + geom_smooth(method="loess", se=FALSE) + ggtitle("NEW.COUNTS + CQN (offset)") + ylab("logFC") + theme(aspect.ratio=1)

plot_grid(fig3, fig3a, fig3b, ncol=3)
```
